Questioning how Researchers Develop and Present Intrusion Detection Systems

### 2014-09-19 docs/questioning.tex
citations for AMNESIA, buffer overflow detectors out
minor corrections
minor changes
availability table

\section{Analysis}

\begin{table*}

@@

\scalebox{0.93}{

@@

	& \bf{Attack Vector} \\

@@

	\multirow{11}{*}{Runtime Tainting}
%	&   {\it Kiriansky et al.~\cite{KBA02}} & {\bf ?},{\bf ?} & $\sim$1\% & {\it binary code} \\
%	&   {\it {\sc cfi}~\cite{ABEL05}} & {\bf ?},{\bf ?} & 0.09--26.78\% & {\it binary code} \\
	&  	{\it SigFree}~\cite{WPLZ10} & 111 & \xmark,\xmark & 10\% & {\it binary code} \\
	&  	{\it {\sc lift}}~\cite{QWLKZW06} & 268 & \tick,\tick & 6.2\% & {\it binary code} \\ 
	&  	{\sc csse}~\cite{PB05} & 312 & \xmark,\xmark & 2--10\% & {\sc sql} \\
	&  	{\it Haldar et al.}~\cite{HCF05} & 177 & {\bf ?},{\bf ?} & \xmark & {\sc sql} \\ 
	&  	{\it SecuriFly}~\cite{MLL05} & 31 & \xmark,\tick & 9--125\% & {\sc sql}, {\sc xss} \\ 
	&  	{\it Xu et al.}~\cite{XBS06} & 297 & \tick,\xmark & 76\% & {\sc sql}, {\sc xss} \\ 
    &  	{\it {\sc wasc}}~\cite{NLC07} & 31 & \xmark,\xmark & 30\% & {\sc sql}, {\sc xss} \\
	&  	{\it {\sc php} Aspis}~\cite{PMP11} & 12 & \xmark,\xmark & 2.2$\times$ & {\sc sql}, {\sc xss}, {\sc php} \\

@@

	& 	{\it Stock et al.}~\cite{SLMS14} & 0 & 0.09\%,\xmark & 7-17\% & {\sc xss} \\

@@

	%& {\it Lekies et al.}~\cite{LSJ13} & & & \\

@@

	&  {\it {\sc sql}rand}~\cite{BK04} & 286 & {\bf ?},{\bf ?} & 6.5{\it ms} & {\sc sql} \\ 

@@

	% &  {\it {\sc csp}} & 0 & {\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\ 
    % &  {\it Google Caja} & 0 & {\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\

@@

    &  {\it TreeHouse}~\cite{IW12} & 18 & {\bf ?},{\bf ?} & 757–--1218ms & {\sc xss} \\
    % &  {\it Dhawan et al.}~\cite{DSG12} & 7 & \xmark,{\bf ?} & 16---114\% & {\sc xss} \\

@@

@@

	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 376 & \tick,\tick & {\bf ?} & {\sc sql} \\ 
	&   {\it {\sc didafit}}~\cite{LLW02} & 85 & \xmark,\xmark & {\bf ?} & {\sc sql} \\
	&   {\it Valeur et al.}~\cite{VMV05} & 226 & 0.37\%,{\bf ?} & 1{\it ms} & {\sc sql} \\
	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & 243 & {\bf ?},{\bf ?} & 3\% & {\sc sql} \\
	& 	{\it Diglossia}~\cite{SMS13} & 3 & \xmark,\xmark  & 13\% & {\sc sql}, No{\sc sql} \\
	& 	{\it {\sc sd}river}~\cite{MS09,MKS09} & 20,5 & \tick,\tick & 39\% & {\sc sql}, {\sc xp}ath \\
	& 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 9,40,1 & \xmark,\xmark  & \xmark & {\sc sql}, {\sc xp}ath \\
	& 	{\it Mattos et al.}~\cite{MSM13} & 2 & \tick,{\bf ?} &  {\bf ?} & {\sc xml}, {\sc xp}ath \\
	& 	{\it {\sc sm}ask}~\cite{JB07} & 27 & \xmark,\xmark & {\bf ?} & {\sc sql}, {\sc xss} \\

@@

    & 	{\it {\sc xss-guard}}~\cite{BV08} & 97 & {\bf ?},\xmark & 5---24\% & {\sc xss} \\

@@

\end{table*}

>>>>

\begin{landscape}
\begin{table}

@@

\scalebox{0.99}{

@@

	& \bf{Attack} \\

@@

	\multirow{9}{*}{Runtime Tainting}
	&  	{\sc csse}~\cite{PB05} & 312 & \xmark,\xmark & 2--10\% & {\sc sql} injection \\
	&  	{\it Haldar et al.}~\cite{HCF05} & 177 & {\bf ?},{\bf ?} & \xmark & {\sc sql} injection \\ 
	&  	{\it SecuriFly}~\cite{MLL05} & 31 & \xmark,\tick & 9--125\% & {\sc sql} injection, {\sc xss} \\ 
	&  	{\it Xu et al.}~\cite{XBS06} & 297 & \tick,\xmark & 76\% & {\sc sql} injection, {\sc xss} \\ 
    &  	{\it {\sc wasc}}~\cite{NLC07} & 31 & \xmark,\xmark & 30\% & {\sc sql} injection, {\sc xss} \\

@@

@@

	&  	{\it {\sc php} Aspis}~\cite{PMP11} & 12 & \xmark,\xmark & 2.2$\times$ & {\sc sql} and {\sc php} injection, {\sc xss} \\
	& 	{\it Stock et al.}~\cite{SLMS14} & 0 & 0.09\%,\xmark & 7--17\% & {\sc xss} \\

@@

	&   {\it {\sc sql}rand}~\cite{BK04} & 286 & {\bf ?},{\bf ?} & 6.5{\it ms} & {\sc sql} injection \\ 

@@

@@

@@

    &   {\it TreeHouse}~\cite{IW12} & 18 & {\bf ?},{\bf ?} & 757–-1218ms & {\sc xss} \\

@@

    &   {\it {\sc didafit}}~\cite{LLW02} & 85 & \xmark,\xmark & {\bf ?} & {\sc sql} injection \\
	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 118,66,376 & \tick,\tick & {\bf ?} & {\sc sql} injection \\ 
	&   {\it Valeur et al.}~\cite{VMV05} & 226 & 0.37\%,{\bf ?} & 1{\it ms} & {\sc sql} injection \\
	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & 243 & {\bf ?},{\bf ?} & 3\% & {\sc sql} injection \\
	& 	{\it {\sc sm}ask}~\cite{JB07} & 27 & \xmark,\xmark & {\bf ?} & {\sc sql} injection, {\sc xss} \\
    & 	{\it {\sc xss-guard}}~\cite{BV08} & 97 & {\bf ?},\xmark & 5--24\% & {\sc xss} \\

@@

	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & 20,8,5 & \tick,\tick & 39\% & {\sc sql} and {\sc xp}ath injection \\
	& 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 9,40,1 & \xmark,\xmark  & \xmark & {\sc sql} and {\sc xp}ath injection \\
	& 	{\it Diglossia}~\cite{SMS13} & 3 & \xmark,\xmark  & 13\% & {\sc sql} and No{\sc sql} injection \\

@@

\end{table}
\end{landscape}

\begin{table*}
\centering
    \begin{threeparttable}
    \begin{small}
\scalebox{0.99}{
    \begin{tabular}{l|c|ccc}
    \hline
    \bf{Approach}
	& \bf{Mechanism}
    & \multicolumn{3}{|c|}{Availability} \\
	&& \bf{Source Code}
	& \bf{Executable}\tnote{4}
	& \bf{Testbed} \\
    \hline
	\multirow{9}{*}{Runtime Tainting}
	&  	{\sc csse}~\cite{PB05} & \xmark,\xmark & 2--10\% & - \\
	&  	{\it Haldar et al.}~\cite{HCF05}  & {\bf ?},{\bf ?} & \xmark & - \\ 
	&  	{\it SecuriFly}~\cite{MLL05}  & \xmark,\tick & 9--125\% & - \\ 
	&  	{\it Xu et al.}~\cite{XBS06}  & \tick,\xmark & 76\% & - \\ 
    &  	{\it {\sc wasc}}~\cite{NLC07} & \xmark,\xmark & 30\% & - \\
	&  	{\it Vogt et al.}~\cite{VFJKKV07}  & \xmark,{\bf ?} & {\bf ?} & - \\
	&   {\it Noxes}~\cite{KKVJ06,KJKV09}  & {\bf ?},{\bf ?},{\bf ?},{\bf ?} & {\bf ?} & - \\
	&  	{\it {\sc php} Aspis}~\cite{PMP11} & \xmark,\xmark & 2.2$\times$ & - \\
	& 	{\it Stock et al.}~\cite{SLMS14} & 0.09\%,\xmark & 7--17\% & - \\
	\hline
	\hline      
	\multirow{3}{*}{{\sc isr}}
	&   {\it {\sc sql}rand}~\cite{BK04}  & {\bf ?},{\bf ?} & 6.5{\it ms} & - \\ 
	&   {\it Noncespaces}~\cite{GC09}  & \tick,\tick &  10.3\% & - \\ 
    &   {\it x{\sc js}}~\cite{APKLM10} & \tick,\tick & 1.6--40{\it ms} & - \\
	\hline
	\hline    
	\multirow{13}{*}{Policy Enforcement}
	&   {\it {\sc dsi}}~\cite{NSS06}  & \xmark,\xmark & 1.85\% & - \\ 
	&   {\it BrowserShield}~\cite{RDWDE07}  & \tick,\tick & 8\% & - \\ 
	&   {\it CoreScript}~\cite{YCIS07} & {\bf ?},{\bf ?} &  {\bf ?} & - \\ 
	&   {\it {\sc met}}~\cite{ELX07} & {\bf ?},{\bf ?} &  {\bf ?} & - \\ 
    &   {\it {\sc beep}}~\cite{TNH07} & \tick,\tick & 14.4\% & - \\
    &   {\it {\sc soma}}~\cite{OWVS08}  & 5,0,0,0 & 5.58\% & - \\
	&   {\it Blueprint}~\cite{LV09} & \tick/\tick & 13.6\% & - \\ 
	&   {\it Phung et al.}~\cite{PSC09} & \xmark,{\bf ?} & 5.37\% & - \\
	&   {\it WebJail}~\cite{VDDPJ11}  & {\bf ?},{\bf ?} & $\sim$7ms & - \\ 
	&   {\it ConScript}~\cite{ML10}  & {\bf ?},{\bf ?} & 7\% & - \\
	&   {\it j{\sc csrf}}~\cite{PS11}  & 2,7,0,0 & 2ms & - \\
    &   {\it TreeHouse}~\cite{IW12}  & {\bf ?},{\bf ?} & 757–-1218ms & - \\
   	&   {\it {\sc js}and}~\cite{AVBPDP12}  & {\bf ?},{\bf ?} & up to 365\% & - \\
	\hline
	\hline  
        \multirow{12}{*}{Training}
    &   {\it {\sc didafit}}~\cite{LLW02}  & \xmark,\xmark & {\bf ?} & - \\
	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & \tick,\tick & {\bf ?} & - \\ 
	&   {\it Valeur et al.}~\cite{VMV05} & 0.37\%,{\bf ?} & 1{\it ms} & - \\
	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & {\bf ?},{\bf ?} & 3\% & - \\
	& 	{\it {\sc sm}ask}~\cite{JB07}  & \xmark,\xmark & {\bf ?} & - \\
	& 	{\it {\sc xssds}}~\cite{JEP08} & \xmark,\xmark & {\bf ?} & - \\
    & 	{\it {\sc xss-guard}}~\cite{BV08} & {\bf ?},\xmark & 5--24\% & - \\
    & 	{\it {\sc swap}}~\cite{WPLKK09} & \tick,\tick & $\sim$180\% & - \\ 
	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & \tick,\tick & 39\% & - \\
	& 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & \xmark,\xmark  & \xmark & - \\
	& 	{\it Diglossia}~\cite{SMS13} & \xmark,\xmark  & 13\% & - \\
	\hline
    \end{tabular}}
    \begin{tablenotes}
	\begin{footnotesize}
       \item[1] {\it Flexibility} indicates if the approach can be adjusted
	in order to detect different {\sc cia} categories.
       \item[4] {\it User Experience} is affected if the mechanism suffers
	from runtime overhead.
	\end{footnotesize}
    \end{tablenotes}
    \caption{Availability of the corresponding mechanisms.}
    \label{tab:comp2}
    \end{small}
    \end{threeparttable}
\end{table*}
